\href{http://www.sigcomm.org/content/ebook}{Recent Advances in Networking}

### 2013-08-08 Compiled/chapter9/Content/introduction.tex
fix typo in chapter9

\paragraph{Low-Power Lossy Networks (LLNs)} According to the IETF's terminology (defined in {\tt draft-ietf-roll-terminology-12}\footnote{An Internet-Draft in the Last Call for becoming an RFC, at the the time of writing this chapter.} \cite{draft_lln}), LLNs are ``typically composed of many embedded devices with limited power, memory, and processing resources interconnected by a variety of links, such as IEEE 802.15.4, LowPower WiFi" \cite{draft_lln}. LLNs are thus a more specific case of MANETs (as defined in the previous paragraph), in which \glslink{router}{routers} typically operate with constraints on processing power, memory, and energy (battery power). Their interconnections are characterized by high loss rates, low data rates, and link instability.  LLNs are comprised of anything from a few dozen to thousands of \glslink{router}{routers}.  Supported traffic flows include point-to-point (between devices inside the LLN), point-to-multipoint (from a central control point to a subset of devices inside the LLN), and multipoint-to-point (from devices inside the LLN towards a central control point). Alternative, but similar terminology is employed in {\tt draft-ietf-lwig-terminology} \cite{bormann13}, which defines the terms ``constrained nodes" and ``constrained networks" with various classes of constraints. \\

>>>>

\paragraph{Low-Power Lossy Networks (LLNs)} According to the IETF's terminology (defined in \cite{draft_lln}), LLNs are ``typically composed of many embedded devices with limited power, memory, and processing resources interconnected by a variety of links, such as IEEE 802.15.4, LowPower WiFi" \cite{draft_lln}. LLNs are thus a more specific case of MANETs (as defined in the previous paragraph), in which \glslink{router}{routers} typically operate with constraints on processing power, memory, and energy (battery power). Their interconnections are characterized by high loss rates, low data rates, and link instability.  LLNs are comprised of anything from a few dozen to thousands of \glslink{router}{routers}.  Supported traffic flows include point-to-point (between devices inside the LLN), point-to-multipoint (from a central control point to a subset of devices inside the LLN), and multipoint-to-point (from devices inside the LLN towards a central control point). Alternative, but similar terminology is employed in {\tt draft-ietf-lwig-terminology} \cite{bormann13}, which defines the terms ``constrained nodes" and ``constrained networks" with various classes of constraints. \\
